Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-30 bbbq_article.tex
Updates from Overleaf

\richel{Geert, ik kan je hulp goed gebruiken bij dit stukje}
Presentation of antigens by MHC-II is important for the activation of
B cells \richel{je bedoelt denk ik T cellen hier?}. 
B cell produce antibodies that recognize only solvent-exposed protein regions,
thus the B cell receptor is inherently unable to present hydrophobic regions.
Our analysis suggests, however, that MHC-II
over-presents TMH regions. A helper T cell thus needs an 
\geert{
  Beter is zeggen dat (1) MHC-II presentatie belangrijk is voor B cell activatie. (2) B cellen antilichamen produceren, en dan antilichamen solvent-exposed protein regions herkennen. (3) Dat onze analyse suggereert HMC-II presentatie voornamelijk andere (TMH of buried) regio's betreft. (4) Dat T helper cellen dus andere delen van antigene eiwitten herkennen (MHC-II gepresenteerd door de B cellen) dan de BCR bindt.
}

>>>>

Presentation of antigens by MHC-II is important for the activation of
B cells, because B cells present peptides in MHC-II to helper T cells.  
Interestingly, the CB cell produce antibodies that recognize only solvent-exposed protein regions,
thus the B cell receptor is inherently unable to present hydrophobic regions.
Our analysis suggests, however, that MHC-II
over-presents TMH regions. A helper T cell thus needs an 
\geert{
  Beter is zeggen dat (1) MHC-II presentatie belangrijk is voor B cell activatie. (2) B cellen antilichamen produceren, en dan antilichamen solvent-exposed protein regions herkennen. (3) Dat onze analyse suggereert HMC-II presentatie voornamelijk andere (TMH of buried) regio's betreft. (4) Dat T helper cellen dus andere delen van antigene eiwitten herkennen (MHC-II gepresenteerd door de B cellen) dan de BCR bindt.
}
